\documentclass{beamer}
\usepackage{hyperref}
\usepackage{subfig}  %% Para incluir subgraficos
\usepackage{media9} % 
\usepackage{url}

\usepackage[spanish, activeacute]{babel}
\usepackage[utf8]{inputenc}


%
\hypersetup{pdfstartview={Fit}, bookmarks=True, pdftitle={SCEC Presentation},
            pdfauthor={Juan Carlos Vergara-Gallego}, pdfsubject={Presentation},
            pdfkeywords={Waves, Elasticity, Numerical Methods, High Performance Computing, BEM}}  % Configure hyperref

%--- New commands ----%
\newcommand{\footref}[1]{\textsuperscript{\ref{#1}}}
\newcommand{\pardiff}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\pardiffd}[2]{\frac{\partial^2 #1}{\partial #2^2}}
%---------------------%

%\usefonttheme[onlymath]{serif}  % Make equations to be in serif fonts
\usefonttheme{serif}  % Make equations to be in serif fonts

\begin{document}


%title
\title[CyberShake] % (optional, only for long titles)
{A Physics-Based Seismic Hazard Model for Southern California}
\subtitle{CyberShake, Southern California Earthquake Center}
\author[Vergara Gallego, Juan Carlos] % (optional, for multiple authors)
{Juan Carlos Vergara Gallego\\ \texttt{\small jvergar2@eafit.edu.co}\\
{\tiny Presentación disponible en: \url{https://github.com/jvergar2/03_SCEC}}}
\institute{Departamento de Ingeniería Civil\\
  Universidad EAFIT}
\date{\today}
\subject{Ingeniería Sísmica}

% Title page
\frame{\titlepage}

% Outline
\begin{frame}
	\frametitle{Outline}
	\tableofcontents
\end{frame}
%


% Introduction about waves in general
\section{Introduction}
\begin{frame}
\frametitle{Introducción}
%
Se presenta un resumen del trabajo que se está adelantando en el "Southern California Earthquake Center"
%
\end{frame}
%
%
\begin{frame}\frametitle{References}
\begin{itemize}
\item Michael A. Slawinski. Waves and rays in Elastic Continua. Second Edition, 2007.
 
\item Wikipedia community. Onda (f\'isica) [on line]. Wikipedia, La enciclopedia libre, 2010 ; 22 November 2010. 

\item George B. Arfken \& Hans. J. Weber. Mathematical Methods for Physicists. Elsevier Academic Press, 6th Edition, San Diego, 2005.
\end{itemize}
\end{frame}



\end{document}

